Rank verification for exponential families

### 2016-04-09 verifying-winner.tex
Typos and grammar partially fixed

Having observed that Trump received the most votes in this poll, we want to ask whether he is actually in the lead in the population of all Iowa Republicans. Intuitively, we would compare Trump to Cruz, as well as the other candidate. This intuitive method however has a few issues.

@@

\item This has a hidden upward selection bias, or ``winner's curse'', as we are only testing this hypothesis as Trump is leading in the polls. In other words, the hypothesis itself is random. Alternatively, we can note that the marginal type I error rate is indeed not so straightfoward. If the null hypothesis is ``$H_0: \text{Leader in polls has most support}$'', then for any distribution $F$ the marginal type I error rate is

@@

Gutmann and Maymin \cite{Gutmann:1987fk} has worked on a similar question where the observations are from a location family, and the location parameters are compared. In contrast, a related paper by Karnnan and Panchapakesan \cite{Karnnan:2009iv} discussed a scale family instead, comparing the scale parameters. Bofinger \cite{Bofinger:1991hv} gave a location-scale family generated by the exponential distribution as well. However, as location-scale families have limited overlap with exponential families, the counterpart question for exponential families have remained unaddressed. Location-scale families assumed independence between observations, while this is not required in exponential families. A follow-up paper by Maymin and Gutmann \cite{Maymin:1992fz} gave a slightly more general result, applicable to more than location-scale families, yet still under the constraints of independence.

@@

Without loss of generality, we will assume $X_1$ is considered largest with the tie-breaking method above in mind. Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed as the sufficient statistic. The distribution is now
$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$

Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
\begin{align*}
p_{ij}\left(x_1, \ldots, x_n\right) & = \PP\left(X_1 \ge x_1 \middle| X_2 = x_2, \ldots, \frac{X_1 + X_j}{2} = \frac{x_1 + x_j}{2}, \ldots, X_n = x_n, A_1\right) \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}} \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t}},
\end{align*}
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the numerator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
\end{itemize}
Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

@@

It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$. After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / m$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be. However, if $X_9$ is the runner-up, then $X_9 / m$ is likely biased upward nearly as much as $X_5$. Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward. By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, takes care of what little bias there is. Indeed, performing a two-tailed test can be viewed as a sort of ``correction for multiplicity'', albeit one that we would have to make even if $n = 2$.

@@

Gupta and Nagel \cite{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
This was achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and select by
\begin{equation}
J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\} \tag{Procedure GN}.
\label{eqn:gn}
\end{equation}
Gupta and Nagel also provided the method to choose $D$, which we implemented.

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $m$ and $n$. For \ref{eqn:gn}, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate for both procedures is controlled at $\alpha$. \ref{eqn:gn} coincides with our test at $n = 2$. However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = \textwidth]{plotMultinomialPower}
\end{center}
\caption{Power curves as a function of $\delta$. The plots in the first row all have $m = 50$ and the second row $m = 250$. The solid line is the power for the selective test and the dashed line Gupta and Nagel's test.}
\label{fig:power}
\end{figure}

@@

We would like to extend the result from multinomials to exponential families. We henceforth focus on exponential distribution taking the form
\begin{equation}
X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).
\label{eqn:exp_family}
\end{equation}
It is reasonable to assume that the family is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped. This corresponds to requiring $g\left(X\right)$ to be symmetric. We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}. But first we define the notion of {\em majorization}.

@@

We prove the ``if'' part first. For any fixed $a$, and $X_1 \ge a$ and $X_2 < a$, we have
$$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).$$
Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$, summing instead if $X$ is a discrete vector, gives
$$\PP\left(X_1 \ge a, X_2 < a\right) \ge \PP\left(X_1 < a, X_2 \ge a\right).$$
Now adding $\PP\left(X_1 \ge a, X_2 \ge a\right)$ to both probabilities gives
$$\PP\left(X_1 \ge a\right) \ge \PP\left(X_2 \ge a\right),$$
meaning that $X_1$ is greater than $X_2$ in stochastic order. The converse follows from swapping the role of $\theta_1$ and $\theta_2$.

@@

\Cref{fig:compare_rays} have both the $p$-values shown on the same diagram. Proving $p_{12} \ge p_{13}$ is the same as proving
$$\frac{B}{A+B} \ge \frac{D}{C+D} ~~~~ \Longleftrightarrow ~~~~ \frac{B}{A} \ge \frac{D}{C}.$$
We will prove so be extending $A$ to include $A^*$ on the diagram. We denote the sum as $A'$. Formally,
\begin{equation}
A' = \int_{-D_{13}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz \ge \int_{-D_{12}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz = A.
\label{eqn:int_extension}
\end{equation}
It is thus sufficient to show that $B \ge D$ and $C \ge A'$.

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[yellow!50] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, below left] {$B$};
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick, ->] (B) -- ++(30:5) node[midway, above left] {$D$};
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$A^*$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$. $A'$ would refer to the sum of $A$ with the dashed line portion labeled as $A^*$, formally explained in \Cref{eqn:int_extension}. The majorization relation is indicated by the dotted line.}
\label{fig:compare_rays}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\coordinate (C3) at ($(B) + (330:5)$);
	\coordinate (C4) at ($(B) + (30:5)$);
	\coordinate (C5) at ($(C3)!(C1)!(C4)$);
	\coordinate (C6) at ($(C3)!(C2)!(C4)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\draw[dashed] (C5) -- (C6) node[midway, above, rotate = -90] {Truncation for $X_j < X_{j-1}$};
	\fill[yellow!50] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
	\node[above] at ($(C2)!0.7!(C6)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick] (B) -- (C3) node[midway, below left] {$B$};
	\fill (C3) circle(2pt);
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick] (B) -- (C4) node[midway, above left] {$D$};
	\fill (C4) circle(2pt);
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$A^*$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$. The dashed line corresponds to extension in \Cref{eqn:int_extension}. The dotted line on the far right is the truncation that enforces $X_j < X_{j-1}$.}
\label{fig:crop_rays}
\end{figure}

@@

The conditioning above indeed holds some significance. The sufficient filtration \cite{Fithian:2015uj} $\mathcal{F}_k$ is given as the $\sigma$-field
\begin{align*}
\mathscr{F}_k & = \sigma\left(M_0\left(X\right), \ldots, M_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
& = \sigma\left(\left\{X_1 > \ldots > X_j > \max_{k>j} X_k\right\}, X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
& = \sigma\left(M_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right),
\end{align*}
which is the conditioning we used just now. Hence the nested sequence of model satisfies the subpath sufficiency principle, and the $p$-values sequence $p_j$ is independent on nulls, as defined in and shown in Theorem 4 of \cite{Fithian:2015uj}. Thus the step-down procedure where we keep rejecting $H_{0j}$ until the first time that $p_j > \alpha$ controls FWER and FDR.

@@

\item Multinomial distribution, e.g.\ the Iowa Republican poll example in \Cref{sec:introduction}.
$$p\left(x\right) \propto \exp\left(x^T \left(\log \pi\right)\right) \frac{1_{\left\{x_1 + \cdots + x_n = m\right\}}}{x_1! \cdots x_n!}$$
Comparing $\pi_i$ is the same $\log \pi_i$, the natural parameters. Note that the multinomial coefficient is naturally Schur-concave. The step-down procedure is applied to verify the position of the other candidates. Note that for a multinomial distribution, the conditioning \Cref{eqn:step_down_law} is equivalent to conditioning only on $M_{j\left(j+1\right)}$. We summarize the test in \Cref{tbl:poll_analysis}.

@@

\item Independent binomials
$$p\left(x\right) \propto \exp\left(x^T \left(\log p\right)\right) \frac{1}{p_1! \left(N-p_1\right)! \cdots p_n! \left(N-p_n\right)!}$$

>>>>

Having observed that Trump received the most votes in this poll, we want to ask whether he is actually in the lead in the population of all Iowa Republicans. Intuitively, we would compare Trump to Cruz, as well as the other candidate. This intuitive method however has a couple of issues.

@@

\item This has a hidden upward selection bias, or ``winner's curse'', as we are only testing this hypothesis as Trump is leading in the polls. In other words, the hypothesis itself is random. Alternatively, we can note that the marginal type I error rate is indeed not so straightforward. If the null hypothesis is ``$H_0: \text{Leader in polls has most support}$'', then for any distribution $F$ the marginal type I error rate is

@@

Gutmann and Maymin \cite{Gutmann:1987fk} have worked on a similar question where the observations are from a location family, and the location parameters are compared. In contrast, a related paper by Karnnan and Panchapakesan \cite{Karnnan:2009iv} discussed a scale family instead, comparing the scale parameters. Bofinger \cite{Bofinger:1991hv} gave a location-scale family generated by the exponential distribution as well. However, as location-scale families have limited overlap with exponential families, the counterpart question for exponential families have remained unaddressed. Location-scale families assumed independence between observations, while this is not required in exponential families. A follow-up paper by Maymin and Gutmann \cite{Maymin:1992fz} gave a slightly more general result, applicable to more than location-scale families, yet still under the constraints of independence.

@@

Without loss of generality, we will assume $X_1$ is considered largest with the tie-breaking method above in mind. Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed as the sufficient statistic. The distribution is now
$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$

Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
\begin{align*}
p_{ij}\left(x_1, \ldots, x_n\right) & = \PP\left(X_1 \ge x_1 \middle| X_2 = x_2, \ldots, \frac{X_1 + X_j}{2} = \frac{x_1 + x_j}{2}, \ldots, X_n = x_n, A_1\right) \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}} \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t}},
\end{align*}
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the denominator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
\end{itemize}
Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

@@

It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$. After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / m$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be. However, if $X_9$ is the runner-up, then $X_9 / m$ is likely biased upward nearly as much as $X_5$. Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward. By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, we take care of what little bias there is. Indeed, performing a two-tailed test can be viewed as a sort of ``correction for multiplicity'', albeit one that we would have to make even if $n = 2$.

@@

Gupta and Nagel \cite{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
This was achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and select by
$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
Gupta and Nagel also provided the method to choose $D$. The subset selection can be modified. Inherently, the event $\left\{J\left(X\right) = \left\{1\right\}\right\}$ is the same as inferring $\pi_1$ is the largest. We thus implemented their test for this purpose.

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $m$ and $n$. For Gupta and Nagel, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate such that both procedures are controlled at $\alpha$. Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = \textwidth]{plotMultinomialPower}
\end{center}
\caption{Power curves as a function of $\delta$. The plots in the first row all have $m = 50$ and the second row $m = 250$. The solid line and the dashed line are the power for the selective test and Gupta and Nagel's test, respectively.}
\label{fig:power}
\end{figure}

@@

We would like to extend the result from multinomials to exponential families. We henceforth focus on exponential distribution taking the form
\begin{equation}
X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).
\label{eqn:exp_family}
\end{equation}
It is reasonable to assume that the family is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped. This corresponds to requiring $g\left(X\right)$ to be symmetric. We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}. But first we recall the notion of {\em majorization}.

@@

We prove the ``if'' part first. For any fixed $a$, and $X_1 \ge a$ and $X_2 < a$, we have $X_1 > X_2$ and
$$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).$$
Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$, summing instead if $X$ is a discrete vector, gives
$$\PP\left(X_1 \ge a, X_2 < a\right) \ge \PP\left(X_1 < a, X_2 \ge a\right).$$
Now adding $\PP\left(X_1 \ge a, X_2 \ge a\right)$ to both probabilities gives
$$\PP\left(X_1 \ge a\right) \ge \PP\left(X_2 \ge a\right),$$
meaning that $X_1$ is greater than $X_2$ in stochastic order. The converse follows from swapping the role of $\theta_1$ and $\theta_2$.

@@

\Cref{fig:compare_rays} has both the $p$-values shown on the same diagram. Proving $p_{12} \ge p_{13}$ is the same as proving
$$\frac{B}{A+B} \ge \frac{D}{C+D} ~~~~ \Longleftrightarrow ~~~~ \frac{B}{A} \ge \frac{D}{C}.$$
We will prove so by extending $A$ to include $\hat{A}$ on the diagram. We denote the sum $A + \hat{A}$ as $A'$. Formally,
\begin{equation}
A' = \int_{-D_{13}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz \ge \int_{-D_{12}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz = A.
\label{eqn:int_extension}
\end{equation}
It is thus sufficient to show that $B \ge D$ and $C \ge A'$.

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[yellow!50] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, below left] {$B$};
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick, ->] (B) -- ++(30:5) node[midway, above left] {$D$};
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\hat{A}$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$. $A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\hat{A}$, formally explained in \Cref{eqn:int_extension}. The majorization relation is indicated by the dotted line.}
\label{fig:compare_rays}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\coordinate (C3) at ($(B) + (330:5)$);
	\coordinate (C4) at ($(B) + (30:5)$);
	\coordinate (C5) at ($(C3)!(C1)!(C4)$);
	\coordinate (C6) at ($(C3)!(C2)!(C4)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\draw[dashed] (C5) -- (C6) node[midway, above, rotate = -90] {Truncation for $X_j < X_{j-1}$};
	\fill[yellow!50] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
	\node[above] at ($(C2)!0.7!(C6)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick] (B) -- (C3) node[midway, below left] {$B$};
	\fill (C3) circle(2pt);
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick] (B) -- (C4) node[midway, above left] {$D$};
	\fill (C4) circle(2pt);
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\hat{A}$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$. The dashed line corresponds to extension in \Cref{eqn:int_extension}. The dotted line on the far right is the truncation that enforces $X_j < X_{j-1}$.}
\label{fig:crop_rays}
\end{figure}

@@

The conditioning above indeed holds some significance. The sufficient filtration \cite{Fithian:2015uj} $\mathscr{F}_k$ is given as the $\sigma$-field
\begin{align*}
\mathscr{F}_k & = \sigma\left(M_0\left(X\right), \ldots, M_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
& = \sigma\left(\left\{X_1 > \ldots > X_j > \max_{k>j} X_k\right\}, X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
& = \sigma\left(M_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right),
\end{align*}
which is the conditioning we used just now. Hence the nested sequence of model satisfies the subpath sufficiency principle, and the $p$-values sequence $p_j$ is independent on nulls, as defined in and shown in Theorem 4 of \cite{Fithian:2015uj}. Thus the step-down procedure where we keep rejecting $H_{0j}$ until the first time that $p_j > \alpha$ controls FWER and FDR.

@@

\item Multinomial distribution, e.g.\ the Iowa Republican poll example in \Cref{sec:introduction}.
$$p\left(x\right) \propto \exp\left(x^T \left(\log \pi\right)\right) \frac{1_{\left\{x_1 + \cdots + x_n = m\right\}}}{x_1! \cdots x_n!}$$
Comparing $\pi_i$ is the same as comparing $\log \pi_i$, the natural parameters. Note that the multinomial coefficient is naturally Schur-concave. The step-down procedure is applied to verify the position of the other candidates. Note that for a multinomial distribution, the conditioning \Cref{eqn:step_down_law} is equivalent to conditioning only on $M_{j\left(j+1\right)}$. We summarize the test in \Cref{tbl:poll_analysis}.

@@

\item Independent binomials
$$p\left(x\right) \propto \exp\left(x^T \left(\log p\right)\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-p_x\right)!}$$
